Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-19 Revision/list.tex
revised manuscript and feedback to comments

\response{Thanks for pointing it out. The labels (a) and (b) are now added in the revised manuscript.   The \textcolor{black}{black} line stands for the realized observations whereas the \textcolor{magenta}{magenta} line stands for the fitted values.} \\

@@

\response{Thanks for pointing it out. We  clarify this in the revised version. The black dots represent the real data. The line in \textcolor{magenta}{magenta} color represents the fitted line of our model.}

@@

You are right about the timing. It can be applicable in many different timing scenarios. Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. It is possible to generalize our method to this situation. \\

@@

\response{There are mainly three decisions to make for an user: to choose 
  \begin{itemize}
    \item among  $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, and $\hat{\alpha}_{\rm wadj}$ 
    \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
    \item The $k$ in the $k$ random draws in LOOCV
  \end{itemize}
  First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution. Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool. Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates. These recommendations are included in Remark 3 at the end of Section 2. \\

>>>>

\response{Thanks for pointing it out. The labels (a) and (b) are now added in the revised manuscript.   The \textcolor{black}{black} line stands for the realized observations whereas the violet line stands for the fitted values.} \\

@@

\response{Thanks for pointing it out. We  clarify this in the revised version. The black dots represent the real data. The line in violet color represents the fitted line of our model.}

@@

You are right about the timing. It can be applicable in many different timing scenarios. Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. It is possible to generalize our method to this situation. \textcolor{red}{Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates.}\\

@@

\response{\textcolor{red}{Thank you for pointing it out. We repolished Section 4 for better readability in the revised manuscript.} \textcolor{red}{We  summarize  our results including preferred user decisions as below. }There are mainly three decisions to make for an user: to choose 
  \begin{itemize}
    \item among  $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, and $\hat{\alpha}_{\rm wadj}$ 
    \item between $\mathcal{B}_f$ and $\mathcal{B}_u$ (see detailed definition in Section 3.2)
    \item The $k$ in the $k$ random draws in LOOCV
  \end{itemize}
  First, $\hat{\alpha}_{\rm adj}$ is usually recommended when we believe the shock is i.i.d from a distribution. Second, $\hat{\alpha}_{\rm IVW}$ is recommended when the time length $T_i$ in the donor pool varies vastly across the donor pool. Third, $\hat{\alpha}_{\rm wadj}$  is recommended when we assume the shocks are from the same family of distribution, and the mean of the shock depends on some covariates. These recommendations are included in Remark 3 at the end of Section 2. \\

### 2021-01-19 Revision/manuscript.tex
revised manuscript and feedback to comments

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, we treat the additive shock effect as an observed random effect, obtained from a distribution of similar shocks, that is parameterized as a conditional fixed effect within an autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting framework, provided that the shock effects from outside data sources arose from the same data generating process as the shock effect under study. For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of shocks from the recent past. Our shock effect setting is also similar to the data generating mechanism that  \cite{tsay1986time} studied for ARMA models. \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses. \red{ I do not understand what the following means, please clarify: Our shock effect of interest is similar to innovational  outliers  but with the difference that it is an additive effect but not on outlier among the innovations.}

@@

In this section we provide justification for our methods based on Monte Carlo simulation. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}. The parameter setup of our simulations is detailed as follows: 
\begin{align*}
  \phi_i &\simiid U(0,1),	\\
  \delta_i &\simiid  \normal{1}{0.5}, \\
  \theta_i &\simiid \normal{0}{1}, \\
  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
  T_i^* &\simiid U(p+4, T_i-1), \\
  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}
\end{align*}
where the $[\cdot]$ operation in the generation of the $T_i$s corresponds to rounding the input to the nearest integer and the discrete uniform distribution is used to generate the $T_i^*$s. The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.

@@

In this section, we discuss two real data examples of post-shock prediction. Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020. This shock relates to an oil price war and the COVID-19 pandemic. Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product. These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent. The adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.

@@

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$. The model of $\alpha_i$ incorporates lagged daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX). The model for $y_{i,t}$ disregards VIX. This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Macbook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. 
\end{enumerate}

@@

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and magenta line represent real data and fitted line, respectively.}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. In recent years, we observe that it takes two or more days (\red{Why is it two or more days and not just two days? How can we be certain that we want the shock effect on November 11th instead of November 12th or some later date?}) for the shock to take effect on the stock price. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. We consider 20 trading days data for the time series of interest and time series in the donor pool. All the estimates will be adjusted for inflation. Since we are interested in the stock price of the day after the release date, consider $D_{i, t} = I(t \in \{T_i^* +1, T_i^*+2\})$. As a result, we consider weighting with respect to  
  \begin{align*}
    \mathbf{X}_1 = \mathbf{x}_{1,T_1^*+1: T_1^*+2}' \quad \text{ and } \quad 
    \mathbf{X}= \begin{pmatrix}
      \mathbf{x}_{2,T_2^*+1: T_2^*+2}' \\ \vdots \\ \mathbf{x}_{n+1,T_{n+1}^*+1: T_{n+1}^*+2}'
    \end{pmatrix},
  \end{align*}
  where $ \mathbf{x}_{i,T_i^*+1: T_i^*+2}\in \reals^{p \times 2}$ denotes the matrix joining both covariate column vectors corresponding to time points $t = T_i^* +1$ and $t = T_i^*+2$. \red{You need to define the space of possible values for possible weighs in this new context, it is not immediately clear what you did.} The model $\mc{M}_2$ is then changed to 
  \begin{align*}
    \mc{M}_2 \colon \begin{array}{l}
  y_{i,t} =\eta_i +\alpha_i  I(t \in \{T_i^* +1, T_i^*+2\}) + \phi_i y_{i, t-1} + \theta_i'\mbf{x}_{i,t} + \varepsilon_{i,t}\\[.2cm]
  \; \alpha_i = \mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}+ \t{\varepsilon}_{i},
\end{array}
  \end{align*}
  where $\delta_i \in \R^{p \times 2}$. \red{The above does not make sense, $\delta_{i}'\mbf{x}_{i, T_i^*+1:T_i^*+2}$ is not a scalar, and $y_{i,t}$ is not a vector, right?  It seems that, as currently written, $\alpha_i$ should be replaced by $\alpha_{i,t}$, for $t = T^*+1, T^*+2$, where it is understood that $\alpha_{i,T^*+1}$ is close to zero. But I am not even sure if that is correct, why is the shock effect for the irrelevant nuisance next day response even considered at all? What did you actually do here?}
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of 15 trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 29th, 2018, and June 3rd, 2019, respectively. We only include the last three Macbook releases in our donor pool because those releases are similar to the current release in the sense that Apple inc. has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019, apple2020}. %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.864, 0.905, 1.129$ for $i = 2, 3, 4$, respectively. We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$. As a result, we observe $\mathbf{W}^* = (0.664, 0.000, 0.336)$ \red{It is still a little confusing where this came from since it is not defined in this setting.} and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 3.674$. It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects. The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.071$, $\hat{\alpha}_{\rm wadj}=1.066$, and $\hat{\alpha}_{\rm IVW} = 1.090$. The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.192$, $0.095$, and $0.091$, respectively. Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk. As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well. The unadjusted forecast misses the post-shock by 1.518 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.447, 0.427, and 0.452 dollars, respectively. Note  that the 1-ahead forecast error for the covariates contribute to some of the forecast risk.

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG3.pdf}
    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and magenta line represent real data and fitted line, respectively.}
    \label{Fig3}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings. The model, under which we verify these claims, is a simple AR(1) model. Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.

@@

In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be extended to more general timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool.

>>>>

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, we treat the additive shock effect as an observed random effect, obtained from a distribution of similar shocks, that is parameterized as a conditional fixed effect within an autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting framework, provided that the shock effects from outside data sources arose from the same data generating process as the shock effect under study. For further differences of assumptions on shocks, our methodology allows for unprecedented shocks and no observation of shocks from the recent past. Our shock effect setting is also similar to the data generating mechanism that  \cite{tsay1986time} studied for ARMA models. \cite{tsay1986time} studied additive outliers that contaminates the data at only one or multiple specific points, and innovational outliers that impact the subsequent responses. Our shock effect of interest is similar to innovational  outliers  in the sense that it is an additive effect in the model of response only at a particular time point but it impacts the subsequent responses through an autoregressive structure.

@@

In this section we provide justification for our methods based on Monte Carlo simulation. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}. The parameter setup of our simulations is detailed as follows: 
\begin{align*}
  \phi_i &\simiid U(0,1),	\\
  \delta_i &\simiid  \normal{1}{0.5^2}, \\
  \theta_i &\simiid \normal{0}{1}, \\
  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
  T_i^* &\simiid \red{U\{p+4, T_i-1\}}, \\
  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
\end{align*}
where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, \red{$U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$  stands for a random variable from continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively}. The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.

@@

In this section, we discuss two real data examples of post-shock prediction. Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020. This shock relates to an oil price war and the COVID-19 pandemic. Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product. These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.  \textcolor{red}{Generalizations of our method are discussed as well. Section \ref{forecasting} allows the shock effect to be decomposed into separable estimable parts,  multiple shock effects to be nested in a time series, and different models for the response and the shock effects. Section \ref{apple} extends the forecasting adjustment at $T_1^*+1$ to $T_1^*+2$, and considers  a different model of the time series of interest  to that of   donor pool. In terms of the results, the adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}

@@

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$. The model of $\alpha_i$ incorporates lagged daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX). The model for $y_{i,t}$ disregards VIX. This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 15, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Macbook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. 
\end{enumerate}

@@

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. Black dots and violet line represent real data and fitted line, respectively.}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. \textcolor{red}{From knowledge from our donor pool (see  (3) Construction of donor pool below), we observe that it takes two days for the shock effect to take hold.} Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020, \red{when we conjecture that the time series of interest would experience a shock}. \red{We collect our data through   \texttt{quantmod} package \citep{ryan2017quantmod} in R.} The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \red{\textbf{Selection of model.}}  We use an AR(1) model to forecast the stock price of Apple Inc. All the estimates will be adjusted for inflation.  We consider $D_{i, t} = I(t = T_i^*+2)$. By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini. Denote this date by $T_{1,\#}$, and the shock effect by $\beta$. We account for this shock effect that is not of our interest in the model by setting 
  \begin{align*}
    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
  \end{align*}
  The model for $y_{i,t}$ is the same as in Section \ref{modelsetup} for $i = 2, \ldots, n+1$.   The model for the shock effect is
  \begin{align*}
    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
  \end{align*}
  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates. We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days. As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool. 
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of \red{25} trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively. We only include the last three Macbook releases in our donor pool because \red{we conjecture that} those releases are similar to the current release in the sense that Apple inc. has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019}; \red{and it is indeed consistent \citep{apple2020}}.  %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.686, 1.688, 1.393$ for $i = 2, 3, 4$, respectively. We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$. As a result, we compute $\mathbf{W}^* = (0.712, 0.000, 0.288)$ and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 2.422$. It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects. The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.256$, $\hat{\alpha}_{\rm wadj}=0.889$, and $\hat{\alpha}_{\rm IVW} = 0.951$. The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.245$, $0.134$, and $0.133$, respectively. Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk. As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well. The unadjusted forecast misses the post-shock by 0.799 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.457, 0.090, and 0.152 dollars, respectively. \red{It appears that covariates weighting with $\hat{\alpha}_{\rm wadj}$ is more successful. It is possible that $\mc{M}_2$ is a good fit for the data. Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.}

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 9cm]{FIG3.pdf}
    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
    \label{Fig3}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings. The model, under which we verify these claims, is a simple AR(1) model. Similar results can be obtained for more general models \red{whose parameter can be estimated unbiasedly}. %such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. 
Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.

@@

In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be extended to more general timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool. \red{The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.}
